### 2016-06-22 filters.tex
cheers
Proof of task#1 and minor changes
Notes

\heading{Syntax.}
Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.   
%
The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.  We write $\mathcal{H} \getsr \Hash$ for this operation.
%
The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
%
The determinisitc query algorithm $\Qry\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
%
We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
%which we denote by writing~$\mathcal{H}$ as a superscript.   
%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
%
%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$ and $\Rep$.

%\heading{Discusssion.}
This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way. We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.

@@

\heading{FP-security of hash-based filters.} \tsnote{NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions.  Not totally sure how to capture this intuition nicely.} 
The traditional notion of soundness for a Bloom filter captures the difficulty of finding false-positives when the attacker is non-adaptive.  Following NY, we consider soundness against adaptive adversaries.  But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$S$. (The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.)   In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over $[U]^n$.

In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.  In the top notion, the hash functions are secret.  This is the setting addressed by NY, and it capture applications in which the ``hash functions'' are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.  
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.  That is, the adversary does not exploit structural features of the hash functions in its attack.  This notion makes it easy to track the query complexity of an attack.

For each experiment, we define an associated advantage notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$, distribution~$\distr{U}{n}$ and adversary~$A$, we define:
\begin{align*}
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
\end{align*}
The probabilities are over the coins of the indicated experiment, and he coins of the adversary.   In all experiments, we track time-complexity~$t$ of~$A$, as well as the number of set-membership ($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In the second, we also track the number of hash-queries $q_{\mathrm{h}}$ that the adversary makes.

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
$S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom).  }
\label{fig:fp-filter}
\end{figure}

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

@@

\heading{Security in multiple-server settings. }  In this section, we consider security notions for settings in which there may be multiple servers, each holding a filter representation of a set.  To allow for each server to embed server-specific information into its representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$ where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.  \tsnote{Still some kinks to be ironed out though.  The current notions sample fresh hash functions for each server.  But in (say) the Squid setting, the same hash functions are used across all Squid instances... maybe it suffices, for that setting, to say that the $\Hash_i$ are all the same, and each simply returns a fixed set of~$k$ hash functions (i.e., deterministic).}  To model insider attacks, we give the adversary the ability to corrupt (adaptively) instances of the filter.  Such attacks capture P2P settings, in which the adversary may join the network as a peer.

>>>>

\heading{Syntax.}
Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.
%
The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
\getsr \Hash$ for this operation.
%
The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
%
The deterministic query algorithm $\Qry\colon \Sigma^m \times U
\rightarrow \bits$ takes a representation $M$ and an element $x \in
U$ and returns a bit.
%
We assume that both $\Rep$ and $\Qry$ have blackbox access to the
functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
%which we denote by writing~$\mathcal{H}$ as a superscript.
%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
%
%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
For correctness, we demand that for all~$S$ of size~$n$ and all $x
\in S$, it holds that $\Prob{\Qry(\Rep(S),x)=1}=1$, where the
probability is over the coins of $\Hash$ and~$\Rep$.

%\heading{Discussion.}
This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way. We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.

@@

\heading{FP-security of hash-based filters.} \tsnote{NY give it in
the private hash setting (sort of); but, intuitively, it should be
hard to find false-positives even if you know that MD5 or SHA-x are
the hash functions.  Not totally sure how to capture this intuition
nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
negligible then a random element is a false positive with noticeable
probability. Beyond that, I think that intuitively it makes sense
that if you want false positives to be hard to find then you need to
make the hash functions secret.} The traditional notion of soundness
for a Bloom filter captures the difficulty of finding false
positives when the attacker is non-adaptive. Following NY, we
consider soundness against adaptive adversaries. But we further
generalize to allow for settings in which the attacker may have some
a priori knowledge about the contents of~$S$. (The Niedermaier et
al.~\cite{xxx} attacks, for example, exploit knowledge about the
distribution of German last names.)   In particular, our notions
take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.

\jknote{We also want to capture the fact that finding the first
false positive should not make it any easier to find subsequent
false positives. This is not really captured by the Naor paper,
either (at least not directly, though it may end up being implied by
their definition).}

In Figure~\ref{fig:fp-filter} we give three distinct notions,
characterized by what access the adversary has to the underlying
hash functions used by the filter.  In the top notion, the hash
functions are secret.  This is the setting addressed by NY, and it
captures applications in which the hash functions are (say) secretly
keyed PRFs, and in which no explicit, external interface to these is
surfaced.
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions
public, but assumes that the adversary only accesses them in a
black-box manner.  That is, the adversary does not exploit
structural features of the hash functions in its attack.  This
notion makes it easy to track the query complexity of an attack, and
also allows us to capture constructions in the random-oracle model.

For each experiment, we define an associated advantage
notion.Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
distribution~$\distr{U}{n}$ and adversary~$A$, we define:
\begin{align*}
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
\end{align*}
The probabilities are over the coins of the indicated experiment,
and the coins of the adversary.   In all experiments, we track the
time-complexity~$t$ of~$A$, as well as the number of set-membership
($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
the second, we also track the number of hash-queries
$q_{\mathrm{h}}$ that the adversary makes.

\jnote{How do we want to define a ``secure'' Bloom filter (even
informally)? Do we want to say that the probability of finding a
false positive is negligible? Or that if we set the FP rate to
$\epsilon$ then the best an attacker can do with $q$ hash queries is
$1-(1-\epsilon)^q$ plus negligible? One thing that is nice about the
NY notion is that you get a ``clean'' definition of security: no
matter how many FPs the attacker has found so far, the probability
that it can output a fresh FP is still $\epsilon$.}

\jnote{What parameters are needed to get negligible $\epsilon$? Are
they reasonable in practice?}

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
} } \caption{False-positive security (soundness) for an
$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
queriable hash functions (middle), and public hash functions
(bottom). \jnote{Could also consider not giving $S$ to the
adversary.} } \label{fig:fp-filter}
\end{figure}

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

@@

\heading{Security in multiple-server settings. }  \jnote{What is the
goal here? If they don't share hash functions, I'm not sure what is
gained by considering this definition.} In this section, we consider
security notions for settings in which there may be multiple
servers, each holding a filter representation of a set.  To allow
for each server to embed server-specific information into its
representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
\tsnote{Still some kinks to be ironed out though.  The current
notions sample fresh hash functions for each server.  But in (say)
the Squid setting, the same hash functions are used across all Squid
instances... maybe it suffices, for that setting, to say that the
$\Hash_i$ are all the same, and each simply returns a fixed set
of~$k$ hash functions (i.e., deterministic).} To model insider
attacks, we give the adversary the ability to corrupt (adaptively)
instances of the filter.  Such attacks capture P2P settings, in
which the adversary may join the network as a peer.
